%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founder \& Lead Software Engineer} % Job title
    {Bytecorp} % Organization
    {Rotterdam, The Netherlands / Kevelaer, Germany} % Location
    {April. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of an automated trading engine for cryptocurrency exchanges.}
        \item {Development and implementation of analysis models used in (self-optimizing) decision making trees.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {Energy Global B.V.} % Organization
    {Rotterdam, The Netherlands} % Location
    {May. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Development of an enterprise application which connects to gas grid operators and conforms to European regulations. \newline The application facilitates portfolio management and trading on the (international) gas grid.}
        \item {Development of a generic XML parser which automatically creates and populates entities (including node relation) from complex documents.}
        \item {Project management for the nationwide AS4 migration (GTS and EDSN).}
        \item {Involved in the hiring process of developers and setting up the development team. Introduced tools to facilitate a faster and better workflow.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (freelance)} % Job title
    {Acapture} % Organization
    {New York, United States of America} % Location
    {Feb. 2015 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of a solution to integrate European payment providers in the Acapture software.}
      \end{cvitems}
    }
  
%---------------------------------------------------------
  \cventry
    {Software Engineer \& Project Manager} % Job title
    {Codebeard} % Organization
    {Rotterdam, The Netherlands} % Location
    {sep. 2014 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project management for clients regarding their technical challenges and online branding.}
        \item {Software and web development on project basis.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {DPDK} % Organization
    {Rotterdam, The Netherlands} % Location
    {Oct. 2012 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of a social media platform using Kohana framework and node.js/socket.io.}
        \item {Development of various Facebook games for customers/brands.}
        \item {Development of a custom backend for the iOS/Android game "Jewel Sprint"}
        \item {Actively tutored junior and medior developers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (freelance)} % Job title
    {Workstreampeople} % Organization
    {Rotterdam, The Netherlands} % Location
    {Sept. 2012 - Oct. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of an iOS app which displays real-time call-center statistics using Microsoft LYNC services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Webstudio MM} % Organization
    {Delft, The Netherlands} % Location
    {Aug. 2011 - Sept. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the LINDA. magazine Android app using Phonegap.}
        \item {Developed a external solution (www.money2.nl) to instantly topup or activate PayPal accounts. This solution is now integrated in PayPal.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software/Sharepoint Engineer} % Job title
    {Workstreampeople} % Organization
    {The Hague, The Netherlands} % Location
    {June. 2008 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a migration plan for Sharepoint 2007 to Sharepoint 2010 for the ING group.}
        \item {Developed a learning portal for NIBC bank using Sharepoint 2007 and Nintex with automated business rules and approval workflow.}
        \item {Developed a C\# web-service which connects the AD and Exchange server to Sharepoint which is used by the NTI customer backend.}
        \item {Developed a QA solution in Sharepoint 2007 with automated approval workflows and document lock-down confirming the mandatory ISO regulations for Q8 and regular oil industry.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
\vspace{20 mm}
